MLExplain

### 2018-05-24 paper.tex
Ajouté une phrase, commit rapide
Ajouté une petite partie sur l'interface web

The frontend is compiled with \emph{js\_of\_ocaml}
\cite{DBLP:journals/spe/VouillonB14}, the compiler of the project
\emph{Ocsigen} \cite{balat:hal-00691710}.

>>>>

The frontend is compiled with \emph{js\_of\_ocaml}
\cite{DBLP:journals/spe/VouillonB14}, the compiler of the project
\emph{Ocsigen} \cite{balat:hal-00691710}. The largest part of the frontend is a
module that serializes the \emph{Typedtree} -- the typed AST of OCaml -- into a
JavaScript object compatible with the backend interpreter's own representation
of the AST. We use the \texttt{compiler-libs} library to do the actual parsing
and typing. We ensure that the typed AST we get is the same as the official
OCaml compiler AST since we use the exact same frontend.

% Toute une partie sur MLExplain lui-même...

\subsection{Web interface changes}

The data structures manipulated by MLExplain are very different from those
manipulated by JSExplain since they don't interpret the same language. This led
us to modify the web interface so that it can recognize the different syntactic
elements of OCaml and pretty print them correctly as well as OCaml values.

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file containing the logic of the
application and the corresponding HTML page.
